Marshall and Olkin-G and Gamma-G family of distribution: properties and applications

### 2022-05-18 paper/paper.tex
Paper in journal layout

\documentclass[12pt,a4paper]{article} %437
\usepackage{revstat-v2}
\usepackage{indentfirst}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}
\makeatletter
\makeatother
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{float}
\usepackage{listings}
%\usepackage[dvips]{graphicx, color}
%\usepackage{subfigure}
%\usepackage[skins,listings,breakable]{tcolorbox}
\usepackage{xcolor}
\usepackage{color}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}

%TCIDATA{OutputFilter=latex2.dll}
%TCIDATA{LastRevised=Friday, February 01, 2008 17:54:39}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}

\setlength\topmargin{-1.5cm} \setlength\oddsidemargin{0.0cm}
\setlength\evensidemargin{0.0cm} \setlength{\textwidth}{15cm}
\setlength{\textheight}{25cm}

%\newtheorem{definition}{Definition}
%\newtheorem{theorem}{Theorem}
%\newtheorem{example}{Example}
%\newtheorem{corollary}{Corollary}
%\newtheorem{lemma}{Lemma}
%\newtheorem{proposition}{Proposition}
%\newenvironment{proof}{{\bf Proof:\ \ }}{\qed}
%\newcommand{\qed}{\rule{0.5em}{1.5ex}}
\newcommand{\bfg}[1]{\mbox{\boldmath $#1$\unboldmath}}
\newcommand{\dse} {\displaystyle}
\newcommand{\real}{{I\!\!R}}
\newcommand{\zern}{{\bf 0}}
\newcommand{\Cn}{{\bf C}}
\newcommand{\dn}{{\bf d}}
\newcommand{\Dn}{{\bf D}}
\newcommand{\Pn}{{\bf P}}
\newcommand{\xn}{{\bf x}}
\newcommand{\Un}{{\bf U}}
\newcommand{\Kn}{{\bf K}}
\newcommand{\Xn}{{\bf X}}
\newcommand{\Vn}{{\bf V}}
\newcommand{\vn}{{\bf v}}
\newcommand{\bn}{{\bf b}}
\newcommand{\an}{{\bf a}}
\newcommand{\cn}{{\bf c}}
\newcommand{\en}{{\bf e}}
\newcommand{\sn}{{\bf s}}
\newcommand{\Bn}{{\bf B}}
\newcommand{\An}{{\bf A}}
\newcommand{\yn}{{\bf y}}
\newcommand{\Yn}{{\bf Y}}
\newcommand{\Zn}{{\bf Z}}
\newcommand{\zn}{{\bf z}}
\newcommand{\Hn}{{\bf H}}
\newcommand{\Gn}{{\bf G}}
\newcommand{\Mn}{{\bf M}}
\newcommand{\fn}{{\bf f}}
\newcommand{\hn}{{\bf h}}
\newcommand{\In}{{\bf I}}
\newcommand{\Fn}{{\bf F}}
\newcommand{\En}{{\bf E}}
\newcommand{\Jn}{{\bf J}}
\newcommand{\Ln}{{\bf L}}
\newcommand{\mn}{{\bf m}}
\newcommand{\rn}{{\bf r}}
\newcommand{\un}{{\bf u}}
\newcommand{\Rn}{{\bf R}}
\newcommand{\Sn}{{\bf S}}
\newcommand{\Tn}{{\bf T}}
\newcommand{\GLn}{{\bf G \bf L}}
\newcommand{\tn}{{\bf t}}
\newcommand{\alpn}{{\mbox{\boldmath $\alpha$}}}
\newcommand{\epsiln}{{\mbox{\boldmath $\epsilon$}}}
\newcommand{\rhn}{{\mbox{\boldmath $\rho$}}}
\newcommand{\betn}{{\mbox{\boldmath $\beta$}}}
\newcommand{\deltn}{{\mbox{\boldmath $\delta$}}}
\newcommand{\sigmn}{{\mbox{\boldmath $\beta$}}}
\newcommand{\gamn}{{\mbox{\boldmath $\gamma$}}}
\newcommand{\Gamn}{{\mbox{\boldmath $\Gamma$}}}
\newcommand{\lamn}{{\mbox{\boldmath $\lambda$}}}
\newcommand{\Lamn}{{\mbox{\boldmath $\Lambda$}}}
\newcommand{\mun}{{\mbox{\boldmath $\mu$}}}
\newcommand{\etn}{{\mbox{\boldmath $\eta$}}}
\newcommand{\tetn}{{\mbox{\boldmath $\theta$}}}
\newcommand{\Tetn}{{\mbox{\boldmath $\Theta$}}}
\newcommand{\Deltn}{{\mbox{\boldmath $\Delta$}}}
\newcommand{\Phin}{{\mbox{\boldmath $\Phi$}}}
\newcommand{\phin}{{\mbox{\boldmath $\phi$}}}
\newcommand{\Psin}{{\mbox{\boldmath $\Psi$}}}
\newcommand{\psin}{{\mbox{\boldmath $\psi$}}}
\newcommand{\Upin}{{\mbox{\boldmath $\Upsilon$}}}
\newcommand{\upin}{{\mbox{\boldmath $\upsilon$}}}
\newcommand{\Sign}{{\mbox{\boldmath $\Sigma$}}}
\newcommand{\Omegn}{{\mbox{\boldmath $\Omega$}}}
\newcommand{\omegn}{{\mbox{\boldmath $\omega$}}}
\newcommand{\eln}{{\mbox{\boldmath $\ell$}}}
\newcommand{\taun}{{\mbox{\boldmath $\tau$}}}

\hyphenation{ge-ne-ra-ted  hy-per-geo-me-tric  cha-rac-te-ri-ze}

\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=cyan,
}

\urlstyle{same}

\begin{document}

\begin{center}
\section*{\centerline {A new family of distributions: properties and applications}}
\vspace{0.3in}
{\large Gauss M. Cordeiro$^a$ , Maria do Carmo S. Lima$^a$ and Pedro Rafael D. Marinho$^b$}\\
%\vspace{0.3in}
%First Version: 27 July 2010\\
%\vspace{0.1in}
%This Version: 27 January 2011\\
\end{center}

\begin{abstract}\noindent
This article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes. The family has only two
extra shape parameters and can be a better model  than other existing classes of distributions. Simulations are performed to verify the
consistency of the estimators. Its flexibility is shown using two real data sets.
\end{abstract}

\vspace{0.5in}
\noindent {\bf Key Words}:  Distribution family;  mathematical properties; simulations; applications.\\ \\
%\noindent {\bf JEL Codes}: C16, G1 \\ \\
\noindent $^{a}$  Department of Statistics, Federal University of Pernambuco, Recife, Brazil.\\
\noindent $^{b}$ Department of Statistics, Federal University of Paraíba, João Pessoa, Brazil.\\
E-mail:\emph{gausscordeiro@de.ufpe.br, maria@de.ufpe.br, pedro.rafael.marinho@gmail.com} \\

@@

\lstinputlisting[language=R, caption={Monte-Carlo simulations for different sample sizes.}, numbers=left,
stepnumber=1,
showspaces=false,
tabsize=4,
basicstyle=\scriptsize,
backgroundcolor=\color{lbcolor},
showstringspaces=false]{new_code_dagum.R}

>>>>

\documentclass[twoside,leqno,11pt]{article}
\usepackage{revstat-v2}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{float}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{color}

\newcommand{\etn}{{\mbox{\boldmath $\eta$}}} 
\hyphenation{ge-ne-ra-ted  hy-per-geo-me-tric  cha-rac-te-ri-ze}

\begin{document}
\thispagestyle{firstpage}

\vspace{-3.2cm}

\noindent
{\footnotesize {\sffamily REVSTAT~~--~~Statistical~~Journal\\[-1pt]
		Volume 0, Number 0, Month 0000,
		000-000}}
% \thepage-\pageref{LastPage}}}   % requires \usepackage{lastpage}

\vspace{1.5cm}
\title{Marshall and Olkin-G and Gamma-G family of distribution: properties and applications
	%\footnote{The opinions expressed in this text are those of the authors and do not necessarily reflect the views of any organization.}
}
\renewcommand{\titleheading}
{Using the ``revstat-v2.sty" Package}  % --- on odd running heads

\author{\authoraddress{Maria do Carmo S. Lima \href{https://orcid.org/0000-0004-8882-8330}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}} 
	{Department of Statistics,
		Federal University of Pernambuco,\\
        Pernambuco, Recife, Brazil
		\ (maria@de.ufpe.br)}
	\\
	\authoraddress{Gauss M. Cordeiro \href{https://orcid.org/0000-0002-3052-6551}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}}
	{Department of Statistics,
		Federal University of Pernambuco,\\
		Pernambuco, Recife, Brazil
		\ (gauss@de.ufpe.br)}
	\\
	\authoraddress{Pedro Rafael D. Marinho \href{https://orcid.org/0000-0003-1591-8300}{\includegraphics[scale=0.08]{ORCID-iD_icon-128x128}}
	\correspondingauthor}
	{Department of Statistics,
		Federal University of Paraíba,\\
		Paraíba, João Pessoa, Brazil
		\ (pedro.rafael.marinho@gmail.com)}
}
\renewcommand{\authorheading}
{Author Pedro Rafael D. Marinho}  % --- on even running heads

%\vspace{0.3in}
%First Version: 27 July 2010\\
%\vspace{0.1in}
%This Version: 27 January 2011\\

%-------------------------------------------------------------------------------
% Just asking LaTeX to effectively do the title...
%-------------------------------------------------------------------------------
\maketitle
%-------------------------------------------------------------------------------
% Just asking LaTeX to numerate lines...
%-------------------------------------------------------------------------------
\setpagewiselinenumbers
\modulolinenumbers[1]
\linenumbers
%%%%%%%%%%%%%%%%%%%%%%%%%% alteracao: Datas %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
~~~~{\small{\sffamily Received:} December 2020 ~~~~~~{\sffamily Revised:} May 2022 ~~~~~~{\sffamily Accepted:} Month 0000}
%%%%%%%%%%%%%%%%%%%%%%%%%% alteracao %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
% Abstract of the article...
%-------------------------------------------------------------------------------
\begin{abstract}
This article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes. The family has only two
extra shape parameters and can be a better model  than other existing classes of distributions. Simulations are performed to verify the
consistency of the estimators. Its flexibility is shown using two real data sets.
\end{abstract}

%-------------------------------------------------------------------------------
% Keywords...
%-------------------------------------------------------------------------------
\begin{keywords}
 Distribution family;  mathematical properties; simulations; applications.
\end{keywords}

%-------------------------------------------------------------------------------
% AMS classifications...
%-------------------------------------------------------------------------------
\begin{ams}
	49A05, 78B26.
\end{ams}

@@

### 2022-05-18 paper/reviews/answers/letter_answers.Rmd
Paper in journal layout

>>>>

- (i) \textcolor{red}{Really, the title of the paper was really bad. We switched to **Marshall and Olkin-G and Gamma-G family of distribution: properties and applications**. We believe that the title now clarifies the paper's proposal better.}
- (ii) \textcolor{red}{Change made. Thanks for the sugestion.}
- (iii) \textcolor{red}{Thanks for the observation. The presentation of tables has been reorganized.}
- (iv) \textcolor{red}{Thanks for the sugestion.We chose to put the code for the simulations in a repository on GitHub. Thus, we considerably reduced the number of pages in the article and made it easier for readers of the material to reuse the code. With the code on GitHub it is also possible to verify the implementation and validate the simulations obtained. To access the codes, see the} [link](https://github.com/prdm0/MOGG/tree/master/code/simulations).

### 2022-05-18 paper/reviews/answers/letter_answers.tex
Paper in journal layout

\documentclass[version=last,12pt,{"/home/prdm0/R/x86_64-pc-linux-gnu-library/4.2/komaletter/rmarkdown/templates/pdf/resources/maintainersDelight"},letterpaper,]{scrlttr2}

@@

\makeatletter
\usepackage{graphicx}
% grffile has become a legacy package: https://ctan.org/pkg/grffile
\IfFileExists{grffile.sty}{%
\usepackage{grffile}
}{}
% set default figure placement to htbp
\def\fps@figure{htbp}
\setkomavar{signature}{Prof.~Dr.~Pedro Rafael D. Marinho\\
(DSc in Statistics from Federal University of Pernambuco)}
\makeatother

@@

\setkomavar{subject}{Marshall and Olkin-G and Gamma-G family of
distribution: properties and applications}
\setkomavar{fromname}{Prof.~Dr.~Pedro Rafael D. Marinho}
\setkomavar{fromaddress}{Department of Statistics\\Federal University of
Paraíba\\João Pessoa, Paraíba - PB, Brazil}

@@

\emph{Response}:
\textcolor{red}{The use of the $A^*$ and $W^*$ statistics, Anderson-Darling and Cramer-von Mises statistics, respectively, corrected by Chen and Balakrishnan, in the paper entitled "A General Purpose Approximate Goodness-of-Fit Test" (see [link](https://www.tandfonline.com/doi/abs/10.1080/00224065.1995.11979578)) are suitable for comparing models that are not necessarily embedded. Therefore, considering the statistics returned by the `goodness.fit` function and considering the distributions compared, we understand that the statistics $A^*$ and $W^*$ are the most suitable for making the comparisons.}

\textcolor{red}{The **AdequacyModel** package was developed by one of the authors of this paper and was published at [https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0221487](https://journals .plos.org/plosone/article?id=10.1371/journal.pone.0221487). A code inspection of the `goodness.fit` function can be done by looking at the [link](https://github.com/prdm0/AdequacyModel/blob/master/R/goodness.fit.R) on GitHub, where it is hosted the development versioning of the package.}

@@

>>>>

\documentclass[version=last,12pt,{"maintainersDelight"},letterpaper,]{scrlttr2}

@@

\makeatletter
\usepackage{graphicx}
% grffile has become a legacy package: https://ctan.org/pkg/grffile
\IfFileExists{grffile.sty}{%
\usepackage{grffile}
}{}
% set default figure placement to htbp
\def\fps@figure{htbp}
\setkomavar{signature}{Prof.~Dr.~Pedro Rafael D. Marinho and co-authors}
\makeatother

@@

\setkomavar{subject}{Marshall and Olkin-G and Gamma-G family of
distribution: properties and applications}
\setkomavar{fromname}{Response letter from the authors}
\setkomavar{fromaddress}{Department of Statistics\\Federal University of
Paraíba\\João Pessoa, Paraíba - PB, Brazil}

@@

\emph{Response}:
\textcolor{red}{The use of the $A^*$ and $W^*$ statistics, Anderson-Darling and Cramer-von Mises statistics, respectively, corrected by Chen and Balakrishnan, in the paper entitled "A General Purpose Approximate Goodness-of-Fit Test" (see   \url{https://www.tandfonline.com/doi/abs/10.1080/00224065.1995.11979578}) are suitable for comparing models that are not necessarily embedded. Therefore, considering the statistics returned by the \texttt{goodness.fit} function and considering the distributions compared, we understand that the statistics $A^*$ and $W^*$ are the most suitable for making the comparisons.}

\textcolor{red}{The  \textbf{AdequacyModel} package was developed by one of the authors of this paper and was published at   \url{https://journals .plos.org/plosone/article?id=10.1371/journal.pone.0221487}. A code inspection of the \texttt{goodness.fit} function can be done by looking at the   \href{https://github.com/prdm0/AdequacyModel/blob/master/R/goodness.fit.R}{link} on GitHub, where it is hosted the development versioning of the package.}

@@

\begin{itemize}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \tightlist
  \item
    \textcolor{red}{Really, the title of the paper was really bad. We switched to \textbf{Marshall and Olkin-G and Gamma-G family of distribution: properties and applications}. We believe that the title now clarifies the paper's proposal better.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{1}
  \tightlist
  \item
    \textcolor{red}{Change made. Thanks for the sugestion.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{2}
  \tightlist
  \item
    \textcolor{red}{Thanks for the observation. The presentation of tables has been reorganized.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{3}
  \tightlist
  \item
    \textcolor{red}{Thanks for the sugestion.We chose to put the code for the simulations in a repository on GitHub. Thus, we considerably reduced the number of pages in the article and made it easier for readers of the material to reuse the code. With the code on GitHub it is also possible to verify the implementation and validate the simulations obtained. To access the codes, see the
    \url{https://github.com/prdm0/MOGG/tree/master/code/simulations}}.
  \end{enumerate}
\end{itemize}
